cardinalR: Generating interesting high-dimensional data structures

### 2025-10-03 paper-cardinalR.Rmd
Updated the positions of the tables

```{r main-tb-html, eval=knitr::is_html_output()}
main_tb |> 
  kable(caption = "The main arguments for `gen_multicluster()`.", col.names = c("Argument", "Type", "Explanation"), linesep = "") 
```

@@

```{r branching-tb-html, eval=knitr::is_html_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Explanation")) 
```

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Explanation")) 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r cube-tb-html, eval=knitr::is_html_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", col.names = c("Function", "Explanation")) 
```

```{r cube-tb-pdf, eval=knitr::is_latex_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r polynomial-tb-html, eval=knitr::is_html_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", col.names = c("Function", "Explanation")) 
```

```{r polynomial-tb-pdf, eval=knitr::is_latex_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r pyramid-tb-html, eval=knitr::is_html_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", col.names = c("Function", "Explanation")) 
```

```{r pyramid-tb-pdf, eval=knitr::is_latex_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r sphere-tb-html, eval=knitr::is_html_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", col.names = c("Function", "Explanation"), linesep = "") 
```

```{r sphere-tb-pdf, eval=knitr::is_latex_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r trefoil-tb-html, eval=knitr::is_html_output()}
trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", col.names = c("Function", "Explanation")) 
```

@@

trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r trigonometric-tb-html, eval=knitr::is_html_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", col.names = c("Function", "Explanation"), linesep = "") 
```

```{r trigonometric-tb-pdf, eval=knitr::is_latex_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

### Generate a Spherical or Hyperspherical Hole Within a Structure

@@

```{r noise-tb-html, eval=knitr::is_html_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", col.names = c("Function", "Explanation")) 
```

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r odd-shape-tb-html, eval=knitr::is_html_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", col.names = c("Function", "Explanation"), linesep = "") 
```

```{r odd-shape-tb-pdf, eval=knitr::is_latex_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "8.5cm")
```

@@

```{r add-tb-html, eval=knitr::is_html_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", col.names = c("Function", "Explanation"), linesep = "") 
```

```{r add-tb-pdf, eval=knitr::is_latex_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

>>>>

```{r main-tb-html, eval=knitr::is_html_output()}
main_tb |> 
  kable(caption = "The main arguments for `gen_multicluster()`.", col.names = c("Argument", "Type", "Explanation"), linesep = "", table.pos = "H") 
```

@@

```{r branching-tb-html, eval=knitr::is_html_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Explanation"), table.pos = "H") 
```

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Explanation"), table.pos = "H") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r cube-tb-html, eval=knitr::is_html_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", col.names = c("Function", "Explanation"), table.pos = "H") 
```

```{r cube-tb-pdf, eval=knitr::is_latex_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r polynomial-tb-html, eval=knitr::is_html_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", col.names = c("Function", "Explanation"), table.pos = "H") 
```

```{r polynomial-tb-pdf, eval=knitr::is_latex_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r pyramid-tb-html, eval=knitr::is_html_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", col.names = c("Function", "Explanation"), table.pos = "H") 
```

```{r pyramid-tb-pdf, eval=knitr::is_latex_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r sphere-tb-html, eval=knitr::is_html_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "H") 
```

```{r sphere-tb-pdf, eval=knitr::is_latex_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r trefoil-tb-html, eval=knitr::is_html_output()}
trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", col.names = c("Function", "Explanation"), table.pos = "H") 
```

@@

trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r trigonometric-tb-html, eval=knitr::is_html_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "H") 
```

```{r trigonometric-tb-pdf, eval=knitr::is_latex_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

### Generate a spherical or hyperspherical hole within a structure

@@

```{r noise-tb-html, eval=knitr::is_html_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", col.names = c("Function", "Explanation"), table.pos = "H") 
```

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r odd-shape-tb-html, eval=knitr::is_html_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "H") 
```

```{r odd-shape-tb-pdf, eval=knitr::is_latex_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "H")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "8.5cm")
```

@@

```{r add-tb-html, eval=knitr::is_html_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "H") 
```

```{r add-tb-pdf, eval=knitr::is_latex_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "H")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```
